---
title: "Example 10"
author: "Thomas Klebel"
date: "4 6 2020"
output: html_document
---

(good tutorial: https://afit-r.github.io/hc_clustering)

# Task desc

```{r, message=FALSE}
input_df <- tibble::tibble(
  company = 1:5,
  avg_unit_cost = c(1, 2.5, 6, 7, 6.2)
)
```


The task is to group the companies according to similarities of unit cost.


## (a) Find the distance matrix!
```{r}
distm <- dist(input_df, method = "euc")
distm
```

## (b) Carry out a hierarchical cluster analysis using single linkage!
```{r}
single <- hclust(distm, method = "single")
```




## (c) Determine the cophenetic matrix and draw a dendrogram!
```{r}
cophenetic(single)
```

```{r}
plot(single)
```


## (d) Which and how many clusters can be found?
Two clusters: (1, 2) & (3, 4, 5)

## (e) Use the random cluster centrs a = 6 and b = 7 to carry out a k-means clustering? After how many steps does this method stop? Does the solution differ from that found by the hierarchical method?
```{r}
# specify centers
custom_centers <- matrix(c(1, 6, 1, 7), byrow = TRUE, ncol = 2)
custom_centers

res_kmeans <- kmeans(input_df, centers = custom_centers)

res_kmeans
res_kmeans$centers
res_kmeans$iter



plot(input_df, col = res_kmeans$cluster)
```


```{r}
# this seems odd: if I only specify one center (i.e. (6, 7) than of course we 
# will only find one cluster)
# 
custom_centers2 <- matrix(c(6, 7), ncol = 2)
custom_centers2

res_kmeans2 <- kmeans(input_df, centers = custom_centers2)

res_kmeans2
res_kmeans2$centers
res_kmeans2$iter



plot(input_df, col = res_kmeans2$cluster)
```

