---
title: "Example 3"
author: "Thomas Klebel"
date: "1 5 2020"
output: html_document
---

# Taske desc
The data contains the quantity of ice cream (CONS) consumed by 29 persons during the months
June to September. Explanantory variables are: INC (income of the person), TEMP (temperature
in F), PRICE (Price). A regression analysis yields the following results:

            Estimate   Std. Error  t value   Pr(>jtj)
---------  ----------  ----------  --------  --------
(Intercept) -6329.81    3105.35     -2.04      0.05
PRICE          23.35      11.48      2.03      0.05
INC            78.08      36.43      2.14      0.04
TEMP            2.82       0.42      6.77      0.00
PRICE:INC      -0.28       0.13      -2.07     0.05

```
Residual standard error: 30.94 on 24 degrees of freedom
Multiple R-squared: 0.7411, Adjusted R-squared: 0.698
F-statistic: 17.18 on 4 and 24 DF, p-value: 8.968e-07
```

# (a) How does the estimated regression model look like?

$y = -6329.81 + 23.35*PRICE + 78.08*INC + 2.82*TEMP + -0.28*PRICE*INC$

# (b) What does -0:28 in column 1 mean?
Der Effekt ist nicht statistisch signifikant!!! Wenn trotzdem interpretieren, 
dann: 
```{r, message=FALSE}
library(tidyverse)
# try out how interaction works
df <- tibble(
  price = seq(1, 100, length.out = 1000),
  inc = runif(1000, 2000, 6000),
  temp = 60,
)


df %>% 
  mutate(inc_group = cut_number(inc, 5),
         pred = -6329.81 + 23.35*price + 78.08*inc + 2.82*temp + -0.28*price*inc) %>% 
  ggplot(aes(price, pred, colour = inc_group)) +
  geom_smooth() +
  theme_bw()
```



Basiseffekte: Je höher einkommen und je höher der Preis, desto mehr wird verkauft.
Aber: insgesamt je höher der Preis, desto weniger wird gekauft, dieser Effekt ist
stärker bei höheren Einkommen. Diese kaufen zwar mehr, reagieren aber "stärker"
auf die Preisänderung.

# (c) Interpret the other parameters, if they are significant.
Höhere Temperatur und höheres Einkommen führen zu mehr verkauftem Eis.

# (d) How large are the variance of the error term and the adjusted R-squared (interpret the figures)?
Varianz des Fehlers: Im Mittel weicht unsere Schätzung um 30.94 von den wahren
Werten ab.


Adjusted R-squared: 0.698, das ist recht hoch, allerdings kann ca. ein drittel
der Varianz nicht erklärt werden, weil mglw. relevante Parameter fehlen.

# (e) What is the confidence interval of the temperature effect?
```{r}
interval <- qnorm(.975) * 0.42
# upper bound:
2.82 +  interval

# lower bound
2.82 - interval
```

