---
title: "Example 2"
author: "Thomas Klebel"
date: "1 5 2020"
output: html_document
---

# Task desc
Diamond prices in Singapur are analysed using the features: Diamond ID, weight in carat, Color
(classes D, E, F, G, H, I), Carity (Klassen IF, SV1, SV2, VVS1, VVS2) and price (in Singapur-
Dollars). The data can be found in “Diamant.csv”.
Carry out a regression analysis to explain the price!

```{r, message=FALSE}
library(tidyverse)
library(patchwork)
theme_set(theme_bw())
diamant <- read_csv("data/Diamant.csv") %>% 
  select(-ID)
```




# (a) How does the model look like, determine the coefficients and interpret them!
```{r}
mod1 <- lm(Preis ~ ., data = diamant)
summary(mod1)
```

- Karat hat starken Einfluss auf Preis, je höher Karat desto höher Preis
- Farbe D (ref) ist die teuerste, die anderen sind günstiger
- Klarkeit IF (ref) ist wiederum am teuersten, die anderen unterschiedlich
günstiger


# (b) Determine the residuals and visualize them graphically!
```{r}
resids_1 <- tibble(
  resids = mod1$residuals,
  index = seq_along(resids)
)

plot_diag <- function(df) {
  p1 <- ggplot(df, aes(resids)) +
    geom_histogram(bins = 40)
  

  p2 <- ggplot(df, aes(index, resids)) +
    geom_point()

  p3 <- ggplot(df, aes(sample = resids)) +
    geom_qq_line() +
    geom_qq()
  
  p1 / (p2 + p3)
}


plot_diag(resids_1)
```




# (c) How do the residuals change, if the log-price is explained and quadratic weight CARAT2 is used in addition to the other explanatory variables?
```{r}
mod2 <- lm(log(Preis) ~ Farbe + Klarheit + Karat * I(Karat^2), data = diamant)
resids_2 <- tibble(
  resids = mod2$residuals,
  index = seq_along(resids)
)

plot_diag(resids_2)

```



# (d) Which price is predicted for a diamond of 0.5 carat with color D in class SV1, which price for color G?
```{r}
tibble(
  Karat = c(.5, .5),
  Farbe = c("D", "G"),
  Klarheit = c("VS1", "VS1")
) %>% 
  predict(mod2, newdata = .) %>% 
  set_names(c("D", "G"))
```


# (e) Find the confidence interval for the coefficient of the weight!
```{r}
confint(mod2) 
```

