---
title: "Example 6"
author: "Thomas Klebel"
date: "9 5 2020"
output: html_document
---

# Task desc
An analysis was carried out to investigate the differences of the alcohol concentration in wines.
For this purpose the following features were measured for 500 wines: tartaric of wine WEINSAEU
(in g=dm3), acetic acid ESSAEU (in g=dm3), citric acid ZTROSAEU (in g=dm3), residual sugar
RESTZUCKER (in g=dm3), chloride CHLORIDE (in g=dm3), specific gravity DICHTE (in
g=cm3), PH, SULFAT (in g=dm3), ALCOHOL (in Vol%), SORT (Type 1, 2, 3, 4). The data are
found in “WeinAlk.csv”.

Carry out a regression analysis to explain ALCOHOL using the independent variables DICHTE,
RESTZUCKER, SORT, CHLORIDE, WEINSAEU und PH durch!

```{r, message=FALSE}
library(tidyverse)
library(patchwork)
theme_set(theme_bw())
alc <- read_csv("data/WeinAlk.csv", locale = locale(decimal_mark = ",")) %>% 
  mutate(SORTE = as.factor(SORTE))
```


```{r}
mod1 <- lm(ALKOHOL ~ DICHTE + RESTZUCKER + SORTE + CHLORIDE + WEINSAEU + PH, 
           data = alc)
```


```{r}
plot_diag <- function(df) {
  p1 <- ggplot(df, aes(.resid)) +
    geom_histogram(bins = 40)
  

  p2 <- ggplot(df, aes(.fitted, .resid)) +
    geom_point()

  p3 <- ggplot(df, aes(sample = .resid)) +
    geom_qq_line() +
    geom_qq() +
    labs(x = NULL, y = NULL)
  
  p1 / (p2 + p3)
}

broom::augment(mod1) %>% 
  plot_diag()
```


# (a) Determine the coefficients of DICHTE and RESTZUCKER?
```{r}
summary(mod1)
```

- Dichte: `r coef(mod1)[["DICHTE"]]`
- Restzucker: `r coef(mod1)[["RESTZUCKER"]]`


# (b) Estiamte ALCOHOL for a wine of SORT = 2 with specific gravity DICHTE = 0.999, RESTZUCKER = 5.6; CHLORIDE = 0.041; PH = 3.21 and WEINSAEU = 6.7?

```{r}
tibble(WEINSAEU = 6.7, 
       RESTZUCKER = 5.6,
       CHLORIDE = .041, 
       DICHTE = .999,
       PH = 3.21, 
       SORTE = "2") %>% 
  predict(mod1, newdata = .)
```


# (c) Find R2 and the variance of the error term?
```{r}
summary(mod1)$r.squared
# variance of error
summary(mod1)$sigma^2
```

# (d) By how much does ALCOHOL change from SORT = 2 to SORT = 3, if all other parameters remain the same?
Differenz ist nicht statistisch signifikant!
```{r}
alc2 <- alc %>% 
  mutate(SORTE = relevel(SORTE, "2"))
mod2 <- update(mod1, data = alc2)
coef(mod2)[["SORTE3"]]
summary(mod2)
```

